Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
LB for general problem: too trivial after all to include

\begin{abstract}
	Distributed   applications,  including  batch  processing, streaming, scale-out databases,
	or machine learning, generate a significant amount of network traffic.
	By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), we can reduce the network load and  improve application performance. 
	However, the communication pattern of different applications is often unknown a priori and may change over time, hence it needs to be learned in an online manner.
	%
	This paper revisits the online 
	balanced repartitioning problem 
	(introduced by Avin et al.~at DISC 2016)
	that asks for an algorithm that strikes
	an optimal tradeoff between the benefits
	of collocation (i.e., lower network load) 
	and its costs (i.e., migrations). 
	%
	Our first contribution is a significantly improved
	lower bound of $\Omega(k\cdot \ell)$ on the
	competitive ratio, where $\ell$ is the number
	of clusters and $k$ is the cluster size,
	even for a scenario in which the communication
	pattern is static and can be perfectly partitioned;
	we also provide an asymptotically tight upper bound 
	of $O(k\cdot \ell)$ for this scenario.
	We contribute an asymptotically tight upper bound
	of $\Theta(\ell)$ for $k=3$,
	for the general model in which the
	communication pattern can change arbitrarily over time.
	We improve the result for $k=2$ by providing a strictly $6$-competitive upper bound for the general model.
	In contrast to most prior work, our algorithms respect all capacity constraints and do not require resource augmentation.

@@

\maciek{the model name is still unclear: in the abstract we mention the repartitioning model introduced by Avin et al.}

@@

\medskip 
In both models, we assume that communication patterns are not known to our algorithms at the beginning.
We measure the~quality of~presented algorithmic solutions by competitive analysis~\cite{borodin-book}, which is well-suited for problems that are online by their nature.
In the competitive analysis, the goal is to~optimize \emph{the competitive ratio} of a given online algorithm: the ratio of its cost to the cost of~an~optimal offline algorithm that knows the whole input sequence in advance.

\maciek{Above definition is the definition of strict competitive ratio. In comparison to non-strict with additive constant. Emphasize? Maybe already use the notion of \OPT}

@@

\noindent
\textbf{General partitioning problem.}
Every lower bound for the learning problem constitutes a converging lower bound for the partitioning problem as the input sequence grows to infinity \maciek{possibly too strong sentence; I need to rethink}.
However, our construction allows for an exact lower bound for partitioning with a~finite input sequence.
To this end, we issue only enough requests until the algorithm collocates the nodes of each ground set (if it never does, we terminate after it pays $k\cdot \ell$).
The construction is oblivious to the choice of the repartitioning cost $\alpha$: we compare the	number of node exchanges of \ALG and \OPT.

>>>>

\begin{abstract}
	Distributed   applications,  including  batch  processing, streaming, scale-out databases,
	or machine learning, generate a significant amount of network traffic.
	By collocating frequently communicating nodes (e.g., virtual machines) on the same clusters (e.g., server or rack), we can reduce the network load and  improve application performance. 
	However, the communication pattern of different applications is often unknown a priori and may change over time, hence it needs to be learned in an online manner.
	%
	This paper revisits the online 
	balanced partitioning problem 
	(introduced by Avin et al.~at DISC 2016)
	that asks for an algorithm that strikes
	an optimal tradeoff between the benefits
	of collocation (i.e., lower network load) 
	and its costs (i.e., migrations). 
	%
	Our first contribution is a significantly improved
	lower bound of $\Omega(k\cdot \ell)$ on the
	competitive ratio, where $\ell$ is the number
	of clusters and $k$ is the cluster size,
	even for a scenario in which the communication
	pattern is static and can be perfectly partitioned;
	we also provide an asymptotically tight upper bound 
	of $O(k\cdot \ell)$ for this scenario.
	For $k=3$, we contribute an asymptotically tight upper bound
	of $\Theta(\ell)$
	for the general model in which the
	communication pattern can change arbitrarily over time.
	We improve the result for $k=2$ by providing a strictly $6$-competitive upper bound for the general model.
	In contrast to most prior work, our algorithms respect all capacity constraints and do not require resource augmentation.

@@

@@

\medskip 
In both models, we assume that communication patterns are not known to our algorithms at the beginning.
We measure the~quality of~presented algorithmic solutions by competitive analysis~\cite{borodin-book}, which is well-suited for problems that are online by their nature.
In the competitive analysis, the goal is to~optimize \emph{the competitive ratio} of a given online algorithm: the ratio of its cost to the cost of~an~optimal offline algorithm that knows the whole input sequence in advance.
We emphasize that all our algorithms have a \emph{strict} competitive ratio (without an additive term).

@@
